env_and_copies_stats

### 2023-04-10 code/analysis_code/stats/3_correlation.qmd
distributuion edits

```{r}
dust<- dust0 %>%
  filter(!is.na(date),
         date %in% as.Date("2022-07-04"):as.Date("2022-07-19")) %>%
  mutate(t7sum = log10(t7sum)) #Log transform Dust conc (as it is not normally distributed)

@@

#### Make Lag data sets by Site

This cleans out non-numeric values, creates site lag from CCA, and producea a final daily plot

@@

@@

```{r, include = FALSE}
b<- cor(bo)
round(b,2) #Round correlation coeff to "x" digits

>>>>

```{r}
dust<- dust0 %>%
  filter(!is.na(date),
         date %in% as.Date("2022-07-04"):as.Date("2022-07-19"))

@@

### Make Lag data sets by Site

This cleans out non-numeric values, creates site lag from CCA, and produces a final daily plot

@@

### Log10 Transform non-normally distributed data and Remove Non-Parametric Variables

Distributions can be found in `1_distribution.qmd`

```{r}
#Blind Oso
bo<-
  bo %>%
  mutate(amm = log10(amm), #Log-transforms data
         din_dip = log10(din_dip),
         doc = log10(doc),
         dust = log10(dust)) %>%
  select(!c(secchi, tn, tdn, don)) #Removes non-parametric data

#Canals
c2<- 
  c2 %>%
  mutate(orthop = log10(orthop),
         dust = log10(dust)) %>%
  select(!c(secchi, nn, sil, doc,toc, tn))

#Gulf
rd<- 
  rd %>%
  mutate(doc = log10(doc),
         toc = log10(toc),
         dust = log10(dust)) %>%
  select(!c(sal, do_mgl, secchi, nn, tn))
```

@@

```{r, include = FALSE}
b<- cor(bo) #Default method = pearson
round(b,2) #Round correlation coeff to "x" digits

### 2023-04-10 code/analysis_code/stats/4_uni_variate.qmd
distributuion edits

fig3<- rd2 %>% ggplot(aes(lag, copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_correlation(method = "pearson")+
  labs(title = "LM DustxCopies (RD+1)",
       x = "log(dust)")
```

>>>>

fig3<- rd2 %>% ggplot(aes(lag, copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_correlation(method = "pearson")+
  labs(title = "LM DustxCopies (RD+1)",
       x = "log(dust)")
fig1
fig2
fig3
```
